[dcpo_demsupport]

### 2020-08-04 paper/dcpo_demsupport.Rmd
clean up

# load(here::here("data", "dcpo_input_update.rda"))
load(here::here("data", "dcpo_theta.rda"))

@@

result_dcpo_1k <- map(df_theta, function(aDataset) {
  plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
        plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
        plm::lag(Region_UN, 1) + plm::lag(muslism_prop_2010, 1) +
        plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset
  )
})

>>>>

load(here::here("data", "dcpo_theta.rda"))

@@

result_dcpo_1k <- map(df_theta, function(aDataset) {
  plm::plm(Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + plm::lag(theta, 1) +
        plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) +
        plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) +
        plm::lag(dependence_pc_di, 1),
    model = "pooling",
    data = aDataset)
})
